\documentclass[french,11pt,a4paper,sans]{moderncv}

\usepackage[frenchb]{babel}
\usepackage[utf8]{inputenc}  
\usepackage[T1]{fontenc}
\RequirePackage{filecontents}


%% \usepackage{apacite}
\usepackage[backend=biber,sorting=ydnt]{biblatex}
\addbibresource{main.bib}

\usepackage[scale=0.75]{geometry}

%% \usepackage{multibib}
%% \newcites{article,book}{{Articles},{Books}}
%% \newcites{journal}{Journal References}

\moderncvstyle{casual}
\moderncvcolor{green}
\usepackage[scale=0.75]{geometry}
\name{Jonathan}{Pastor}
\phone[fixed]{+33 6 58 21 09 06}
\email{jonathan.pastor@me.com}
\homepage{jonathan.pastor.fr}
\social[github]{badock}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle


\section{Ph.D thesis}
\cvitem{title}{\emph{Contributions to massively distributed Cloud Computing infrastructures.}}
\cvitem{supervisors}{Frédéric Desprez and Adrien Lebre}
\cvitem{defense}{October 2016}

\section{Education}
\cventry{2012--2016}{Ph.D, Computer Science}{ASCOLA - Lina - Inria}{Nantes}{\textit{}}{Designed a prototype of a fully distributed OpenStack manager leveraging Redis. This prototype has been presented during the OpenStack summit (Austin, 2016).}  % arguments 3 to 6 can be left empty
\cventry{2009--2012}{Master of Science, Computer Science}{Ecole des Mines de Nantes}{Nantes}{\textit{Engineering degree}}{}
\cventry{2009--2012}{Bachelor, Computer Science}{Université de Nantes}{Nantes}{\textit{}}{}


\section{Professional Experience}

\subsection{Research}
\cventry{August 2017--July 2018}{Research Software Engineer}{Stack team}{IMT Atlantique}{}{Implementation of SeDuCe, a testbed for the power and thermal profiling of datacenters. Meanwhile I was also engineer on the Grid'5000 testbed, in charge of the clusters located in  Nantes.}
\cventry{February 2016--December 2016}{Research Software Developer}{Nimbus team}{University of Chicago/Argonne National Laboratory}{}{Worked on the implementation of the Chameleon infrastructure and on a software that manages the lifecycle of clusterized software deployed on academic cloud computing infrastructures.}
\cventry{October 2012--October 2016}{Ph.D thesis}{ASCOLA}{Nantes}{}{Contributions to massively distributed Cloud Computing infrastructures.}

\subsection{Internships}
\cventry{February--August2012}{Research internship}{ASCOLA}{Nantes}{}{Participation to the development of a Chemical Programming research project.}
\cventry{May--August 2011}{Javascript/ActionScript development}{Accenture}{Riga (Latvia)}{}{}
\cventry{July 2010}{Worker on Mainframes assembly-lines}{IBM}{Montpellier}{}{}
\cventry{July 2009}{Javascript/XUL development}{Carra-consulting}{Nantes}{}{}


\section{Computer skills}
\cvitem{Systems}{OpenStack (Nova, Ironic and Blazar), Grid'5000, UNIX, Redis, MySQL}
\cvitem{Programming languages}{Python, Shell, Java, Scala/Akka, Arduino, C/C++, R language\newline Web programming}


\section{Languages}
\cvdoubleitem{French}{Native}{English}{Professional}
\cvdoubleitem{German}{Scholar}{Spanish}{Basics}
%% \cvdoubleitem{Russian}{Learning basics}{}{}


\section{Research activity}

\subsection{Awards}
\cventry{June 2014}{Grid'5000 large scale challenge}{1st prize}{Grid'5000 Spring
  School 2014}{Ecole normale supérieure de Lyon}{The experiment conducted with
  Laurent Pouilloux got the first prize at the large scale challenge. During
  this experiment we used DVMS and the Vivaldi algorithm to deploy and schedule
  1700 VMs over a multi-site infrastructure.}


\subsection{Research Interests}
\cvitem{Cloud Computing}{Geographically distributed  OpenStack, Cloud Computing infrastructures.}
\cvitem{Distributed computing}{Internet of things, Distributed algorithms, concurrency, fault-tolerance.}

\subsection{Publications}
\nocite{*}

%% \bibliographystyle{ieeetr}
%% \bibliography{main}

\printbibliography[prefixnumbers={A},keyword=J,title={Journal},heading=subbibliography]

\printbibliography[prefixnumbers={A},keyword=A,title={Articles},heading=subbibliography]


\printbibliography[prefixnumbers={P},type=inproceedings,title={International conferences},
                   heading=subbibliography, notkeyword={confnat}]
                   

\printbibliography[prefixnumbers={P},type=inproceedings,title={French conferences},
                   heading=subbibliography, keyword={confnat}]

\printbibliography[prefixnumbers={R},type=report,title={Reports},heading=subbibliography]

\end{document}
